Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
more stainless output

The Stainless output again:
\begin{lstlisting}[style=stainless]
  [Warning ] Found counter-example:
  [Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
  [Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
\end{lstlisting}

@@

\begin{lstlisting}[style=scala]
  sealed abstract class Number extends BasicArithmetic[Int64] {
    override def +(num: Int64): Int64 = apply(checkResult(underlying + num.underlying))

    private def checkResult(result: BigInt): BigInt = {
      require(
        result <= BigInt("9223372036854775807")
        && result >= BigInt("-9223372036854775808")
      )
      result
    }
  }
\end{lstlisting}

>>>>

Stainless output now: \todo{kai special chars again}
% \begin{lstlisting}[style=stainless][Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
%   [  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
%   [  Info  ] Cache hit: 'postcondition' VC for + @12:3...
%   [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
%   [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   bigInt: BigInt -> -9223372036854775809
%   [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
%   [Warning ]   thiss: Number -> Int64Impl(1)
%   [  Info  ]   ┌───────────────────┐
%   [  Info  ] ╔═╡ stainless summary ╞═════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
%   [  Info  ] ║ └───────────────────┘                                                                                                                                                                             ║
%   [  Info  ] ║ +      postcondition                                                 valid from cache            ../../../../../bin/../src/main/scala/addition/modified/currency/CurrencyUnits.scala:12:3   1.266 ║
%   [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  ../../../../../bin/../src/main/scala/addition/modified/number/NumberType.scala:17:36       0.089 ║
%   [  Info  ] ║ apply  adt invariant                                                 valid from cache            ../../../../../bin/../src/main/scala/addition/modified/currency/CurrencyUnits.scala:34:39  0.194 ║
%   [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  ../../../../../bin/../src/main/scala/addition/modified/number/NumberType.scala:62:38       0.348 ║
%   [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
%   [  Info  ] ║ total: 4    valid: 2    (2 from cache) invalid: 2    unknown: 0    time:   1.897                                                                                                                  ║
%   [  Info  ] ╚═══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
%   [  Info  ] Shutting down executor service.
% \end{lstlisting}

@@

\begin{lstlisting}[style=scala]
sealed abstract class Number {
  /** The underlying scala number used to to hold the number */
  protected def underlying: BigInt

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): BigInt = {
    require(
          result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"))
    result
  }
}
\end{lstlisting}
